Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-11-17 talk/pepm2011/paper.tex
more comments

To evaluate our allocation removal algorithm, we look at the effectiveness when
used in the generated tracing JIT of PyPy's Python interpreter. This interpreter
is a full implementation of Python 2.5 language semantics and is about 30'000
lines of RPython code.

@@

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the treatment of partially static data structures
was part of partial evaluation of Prolog programs from the early stages
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again, completely disappear in the
residual program. This is similar to what our optimization does for an
imperative language.
In functional programming this idea was introduced as
 constructor specialisation by Mogensen \cite{mogensen_constructor_1993}.
\reva{I'd refer here to
  deforestation (by Philip Wadler) and "short cut
  deforestation" by Andrew Gill, John Launchbury, and Simon L 
  Peyton Jones}

>>>>

To evaluate our allocation removal algorithm, we look at the effectiveness when
used in the generated tracing JIT of PyPy's Python interpreter. This interpreter
is a full implementation of Python 2.5 language semantics and is about 30,000
lines of RPython code.

@@

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the treatment of partially static data structures
was part of partial evaluation of Prolog programs from the early stages
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again, completely disappear in the
residual program. This is similar to what our optimization does for an
imperative language.
In functional programming this idea was introduced as
 constructor specialisation by Mogensen \cite{mogensen_constructor_1993}.
\reva{I'd refer here to
  deforestation (by Philip Wadler) and "short cut
  deforestation" by Andrew Gill, John Launchbury, and Simon L 
  Peyton Jones}
\revb{cite and relate to: boxing analysis,
soft typing, dynamic typing, etc (by various authors: Henglein, Cartright, Felleisen,
Leroy)}
